---
title: "Linear Regression Model To Predict Car Price "
output: html_notebook
---

# Numerical Dataset
## Split the dataset
```{r}
library(caTools)

#make this example reproducible
set.seed(4)
#num_df <- read.csv(file = '/Users/chrisguan/Documents/Regression/final_project/Num_only/num_df.csv')

df <- read.csv(file = '/Users/chrisguan/Documents/Regression/final_project/cleaned_df.csv')

#use 90% of dataset as training set and 10% as test set
sample <- sample.split(df, SplitRatio = 0.9)
train <- subset(df, sample == TRUE)
test <- subset(df, sample == FALSE)
```


## Train Raw Model
```{r}
fm =lm(price~.,data=train)
summary(fm)
plot(fm)
```
94.17% of variance in the dependent variable (y) that can be explained by the independent variables (x).

### Cleaned Full Model With Log
```{r}
loig_fm =lm(log(price)~.,data=train)
summary(loig_fm)
plot(loig_fm)
```


```{r}
attach(train) 
europe=ifelse(CarName=='europe',1,0)
america=ifelse(CarName=="america",1,0)
asian=ifelse(CarName=="asian",1,0)

gas=ifelse(fueltype=="gas",1,0)
diesel=ifelse(fueltype=="diesel",1,0)

std=ifelse(aspiration=="std",1,0)
turbo=ifelse(aspiration=="turbo",1,0)

hatchback=ifelse(carbody=="hatchback",1,0)
sedan=ifelse(carbody=="sedan",1,0)
wagon=ifelse(carbody=="wagon",1,0)
convertible=ifelse(carbody=="convertible",1,0)
hardtop=ifelse(carbody=="hardtop",1,0)

rwd=ifelse(drivewheel=="rwd",1,0)
fwd=ifelse(drivewheel=="fwd",1,0)
fourwd=ifelse(drivewheel=='4wd',1,0)

front=ifelse(enginelocation=="front",1,0)
rear=ifelse(enginelocation=="rear",1,0)

mpfi=ifelse(fuelsystem=="mpfi",1,0)
bbl2=ifelse(fuelsystem=='2bbl',1,0)
mfi=ifelse(fuelsystem=="mfi",1,0)
bbl1=ifelse(fuelsystem=='1bbl',1,0)
spfi=ifelse(fuelsystem=="spfi",1,0)
bbl4=ifelse(fuelsystem=='4bbl',1,0)
idi=ifelse(fuelsystem=="idi",1,0)
spdi=ifelse(fuelsystem=="spdi",1,0)

dohc=ifelse(enginetype=="dohc",1,0)
ohcv=ifelse(enginetype=="ohcv",1,0)
mfi=ifelse(enginetype=="mfi",1,0)
ohc=ifelse(enginetype=="ohc",1,0)
l=ifelse(enginetype=="l",1,0)
rotor=ifelse(enginetype=="rotor",1,0)
ohcf=ifelse(enginetype=="ohcf",1,0)
dohcv=ifelse(enginetype=="dohcv",1,0)

small=ifelse(cylindernumber=="small",1,0)
middle=ifelse(cylindernumber=="middle",1,0)
large=ifelse(cylindernumber=="large",1,0)
```

```{r}
test
```

```{r}
test$europe=ifelse(test$CarName=='europe',1,0)
test$america=ifelse(test$CarName=="america",1,0)
test$asian=ifelse(test$CarName=="asian",1,0)

test$gas=ifelse(test$fueltype=="gas",1,0)
test$diesel=ifelse(test$fueltype=="diesel",1,0)

test$std=ifelse(test$aspiration=="std",1,0)
test$turbo=ifelse(test$aspiration=="turbo",1,0)

test$hatchback=ifelse(test$carbody=="hatchback",1,0)
test$sedan=ifelse(test$carbody=="sedan",1,0)
test$wagon=ifelse(test$carbody=="wagon",1,0)
test$convertible=ifelse(test$carbody=="convertible",1,0)
test$hardtop=ifelse(test$carbody=="hardtop",1,0)

test$rwd=ifelse(test$drivewheel=="rwd",1,0)
test$fwd=ifelse(test$drivewheel=="fwd",1,0)
test$fourwd=ifelse(test$drivewheel=='4wd',1,0)

test$front=ifelse(test$enginelocation=="front",1,0)
test$rear=ifelse(test$enginelocation=="rear",1,0)

test$mpfi=ifelse(test$fuelsystem=="mpfi",1,0)
test$bbl2=ifelse(test$fuelsystem=='2bbl',1,0)
test$mfi=ifelse(test$fuelsystem=="mfi",1,0)
test$bbl1=ifelse(test$fuelsystem=='1bbl',1,0)
test$spfi=ifelse(test$fuelsystem=="spfi",1,0)
test$bbl4=ifelse(test$fuelsystem=='4bbl',1,0)
test$idi=ifelse(test$fuelsystem=="idi",1,0)
test$spdi=ifelse(test$fuelsystem=="spdi",1,0)

test$dohc=ifelse(test$enginetype=="dohc",1,0)
test$ohcv=ifelse(test$enginetype=="ohcv",1,0)
test$mfi=ifelse(test$enginetype=="mfi",1,0)
test$ohc=ifelse(test$enginetype=="ohc",1,0)
test$l=ifelse(test$enginetype=="l",1,0)
test$rotor=ifelse(test$enginetype=="rotor",1,0)
test$ohcf=ifelse(test$enginetype=="ohcf",1,0)
test$dohcv=ifelse(test$enginetype=="dohcv",1,0)

test$small=ifelse(test$cylindernumber=="small",1,0)
test$middle=ifelse(test$cylindernumber=="middle",1,0)
test$large=ifelse(test$cylindernumber=="large",1,0)
```


```{r}
model<-lm(log(price) ~ wheelbase + carlength + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + peakrpm + citympg + highwaympg+ 
            europe + america + asian + gas + diesel + std + turbo +
            hatchback + sedan + wagon + convertible + hardtop +
            rwd + fwd + fourwd + front + rear +
            mpfi+bbl2+mfi+bbl1+spfi+bbl4+idi+ spdi+
            dohc+ohcv+mfi+ohc+l+rotor+ohcf+dohcv+
            small + middle + large, data= train)
summary(model)
```

```{r}
model1<-lm(log(price) ~ wheelbase + carlength + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + peakrpm + citympg + highwaympg + 
            europe + america  + gas + std +
            hatchback + sedan + wagon + convertible +
            rwd + fwd + front +
            mpfi+bbl2+bbl1+spfi+bbl4+ spdi+
            dohc+ohcv+ohc+l+rotor+ohcf+
            small + middle, data= train)
summary(model1)
```

```{r}
plot(model1)
```



## Manually Use Backward Selection Based on P-value To Find The Best Model
#### Remove carlength
```{r}
model2<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + peakrpm + citympg + highwaympg + 
            europe + america  + gas + std +
            hatchback + sedan + wagon + convertible +
            rwd + fwd + front +
            mpfi+bbl2+bbl1+spfi+bbl4+ spdi+
            dohc+ohcv+ohc+l+rotor+ohcf+
            small + middle, data= train)
summary(model2)
```


#### Remove mpfi
```{r}
model3<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + peakrpm + citympg + highwaympg + 
            europe + america  + gas + std +
            hatchback + sedan + wagon + convertible +
            rwd + fwd + front +
            bbl2+bbl1+spfi+bbl4+ spdi+
            dohc+ohcv+ohc+l+rotor+ohcf+
            small + middle, data= train)
summary(model3)
```


#### Remove l
```{r}
model4<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + peakrpm + citympg + highwaympg + 
            europe + america  + gas + std +
            hatchback + sedan + wagon + convertible +
            rwd + fwd + front +
            bbl2+bbl1+spfi+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model4)
```


#### Remove bbl1
```{r}
model5<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + peakrpm + citympg + highwaympg + 
            europe + america  + gas + std +
            hatchback + sedan + wagon + convertible +
            rwd + fwd + front +
            bbl2+spfi+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model5)
```



#### Remove america
```{r}
model6<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + peakrpm + citympg + highwaympg + 
            europe + gas + std +
            hatchback + sedan + wagon + convertible +
            rwd + fwd + front +
            bbl2+spfi+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model6)
```


#### Remove hatchback
```{r}
model7<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + peakrpm + citympg + highwaympg + 
            europe + gas + std +
            sedan + wagon + convertible +
            rwd + fwd + front +
            bbl2+spfi+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model7)
```

#### Remove wagon
```{r}
model8<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + peakrpm + citympg + highwaympg + 
            europe + gas + std +
            sedan + convertible +
            rwd + fwd + front +
            bbl2+spfi+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model8)
```

#### Remove spfi
```{r}
model9<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + peakrpm + citympg + highwaympg + 
            europe + gas + std +
            sedan + convertible +
            rwd + fwd + front +
            bbl2+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model9)
```

#### Remove peakrpm
```{r}
model10<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + citympg + highwaympg + 
            europe + gas + std +
            sedan + convertible +
            rwd + fwd + front +
            bbl2+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model10)
```


#### Remove fwd
```{r}
model11<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            boreratio + stroke + compressionratio + horsepower + citympg + highwaympg + 
            europe + gas + std +
            sedan + convertible +
            rwd + front +
            bbl2+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model11)
```


#### Remove boreratio
```{r}
model12<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            stroke + compressionratio + horsepower + citympg + highwaympg + 
            europe + gas + std +
            sedan + convertible +
            rwd + front +
            bbl2+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model12)
```

#### Remove std
```{r}
model13<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            stroke + compressionratio + horsepower + citympg + highwaympg + 
            europe + gas +
            sedan + convertible +
            rwd + front +
            bbl2+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model13)
```

#### Remove highwaympg
```{r}
model14<-lm(log(price) ~ wheelbase + carwidth + curbweight + enginesize + 
            stroke + compressionratio + horsepower + citympg + 
            europe + gas +
            sedan + convertible +
            rwd + front +
            bbl2+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model14)
```

#### Remove wheelbase
```{r}
model15<-lm(log(price) ~ carwidth + curbweight + enginesize + 
            stroke + compressionratio + horsepower + citympg + 
            europe + gas +
            sedan + convertible +
            rwd + front +
            bbl2+bbl4+ spdi+
            dohc+ohcv+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model15)
```

#### Remove ohcv
```{r}
model16<-lm(log(price) ~ carwidth + curbweight + enginesize + 
            stroke + compressionratio + horsepower + citympg + 
            europe + gas +
            sedan + convertible +
            rwd + front +
            bbl2+bbl4+ spdi+
            dohc+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model16)
```

#### Remove bbl4
```{r}
model17<-lm(log(price) ~ carwidth + curbweight + enginesize + 
            stroke + compressionratio + horsepower + citympg + 
            europe + gas +
            sedan + convertible +
            rwd + front +
            bbl2+ spdi+
            dohc+ohc+rotor+ohcf+
            small + middle, data= train)
summary(model17)
```

#### Remove middle
```{r}
model18<-lm(log(price) ~ carwidth + curbweight + enginesize + 
            stroke + compressionratio + horsepower + citympg + 
            europe + gas +
            sedan + convertible +
            rwd + front +
            bbl2+ spdi+
            dohc+ohc+rotor+ohcf+
            small, data= train)
summary(model18)
```

#### Remove ohcf
```{r}
model19<-lm(log(price) ~ carwidth + curbweight + enginesize + 
            stroke + compressionratio + horsepower + citympg + 
            europe + gas +
            sedan + convertible +
            rwd + front +
            bbl2+ spdi+
            dohc+ohc+rotor+
            small, data= train)
summary(model19)
```

#### Remove citympg
```{r}
model20<-lm(log(price) ~ carwidth + curbweight + enginesize + 
            stroke + compressionratio + horsepower + 
            europe + gas +
            sedan + convertible +
            rwd + front +
            bbl2+ spdi+
            dohc+ohc+rotor+
            small, data= train)
summary(model20)
```

#### Remove spdi
```{r}
model21<-lm(log(price) ~ carwidth + curbweight + enginesize + 
            stroke + compressionratio + horsepower + 
            europe + gas +
            sedan + convertible +
            rwd + front +
            bbl2+
            dohc+ohc+rotor+
            small, data= train)
summary(model21)
```

### Double Check Feature Selection By Using olsrr Package
```{r}
BWDfit<-ols_step_backward_p(model1)
BWDfit
```
```{r}
summary(model1)
```

### Assumption
The residuals vs fitted scatter plot shows that the points are not randomly permeate on the graph. 
This indicates that there are some other patterns we haven't captured.
Also heteroskedasticity What is heteroskedasticity. This means that the least-squared estimators are no longer BLUE.
There are other estimators which are linear and unbiased which more frequently than least-squared will get closer to the true population parameters. 
```{r}
plot(model21)
```


### F-Test check ANOVA Table
Ho: All unselected numerical variables = 0 VS Ha: Not Ho
The result shows we fail to reject Ho. That indicates that the 7 unselected numerical can be reduced.
```{r}
anova(model1, model21)

n = 178
p = 37
k = 18

ssefm = exp(2.7641)
sserm = exp(2.9654)

nume = (sserm-ssefm)/(p+1-k)
den = ssefm/(n-p-1)

f = nume / den
f_alpha = 2.10

f > f_alpha
```



### Breusch Pagan Test
```{r}
ols_test_breusch_pagan(model21)
```

### Collinearity Diagnostics
```{r}
ols_coll_diag(model21)
```

### Remove VIF Higher than 10?
#### Remove gas
```{r}
model22<-lm(log(price) ~ carwidth + curbweight + enginesize + 
            stroke + compressionratio + horsepower + 
            europe +
            sedan + convertible +
            rwd + front +
            bbl2+
            dohc+ohc+rotor+
            small, data= train)
ols_coll_diag(model22)
summary(model22)
```

#### Remove compressionratio
```{r}
model23<-lm(log(price) ~ carwidth + curbweight + enginesize + 
            stroke + horsepower + 
            europe +
            sedan + convertible +
            rwd + front +
            bbl2+
            dohc+ohc+rotor+
            small, data= train)
ols_coll_diag(model23)
summary(model23)
```

#### Remove dohc
```{r}
model24<-lm(log(price) ~ carwidth + curbweight + enginesize + 
            stroke + horsepower + 
            europe +
            sedan + convertible +
            rwd + front +
            bbl2+
            ohc+rotor+
            small, data= train)
ols_coll_diag(model24)
summary(model24)
```

#### Remove enginesize
```{r}
model25<-lm(log(price) ~ carwidth + curbweight + 
            stroke + horsepower + 
            europe +
            sedan + convertible +
            rwd + front +
            bbl2+
            ohc+rotor+
            small, data= train)
ols_coll_diag(model25)
summary(model25)
```

#### Remove europe
```{r}
model26<-lm(log(price) ~ carwidth + curbweight + 
            stroke + horsepower + 
            sedan + convertible +
            rwd + front +
            bbl2+
            ohc+rotor+
            small, data= train)
ols_coll_diag(model26)
summary(model26)
plot(model26)
```


```{r}
ols_coll_diag(model26)
```


```{r}
plot(model26)
```


```{r}
model26_no_log<-lm(price ~ carwidth + curbweight + 
            stroke + horsepower + 
            sedan + convertible +
            rwd + front +
            bbl2+
            ohc+rotor+
            small, data= train)
ols_coll_diag(model26_no_log)
summary(model26_no_log)
plot(model26_no_log)
```

```{r}
train
```

### Prediction Interval
We are 95% confident that the price for the car with the information above will have a price between 17377.82 and 19009.76.

### Test Model 26
```{r}
p <- predict(model26, test)

t = exp(predict(model26, test, interval = "prediction"))
t

test["model26_pred"] =round(exp(p),0)
test["model26_pred_lwr"] = t[,2]
test["model26_pred_upr"] = t[,3]

test[,c('model26_pred', "price","model26_pred_lwr", "model26_pred_upr")]

plot(test$predicted_model_26, test$price)
```







# Other Attemptions
#### Solution1: Remove Outlier
```{r}
cooksd <- cooks.distance(num_fit)

plot(cooksd, pch="*", cex=2, main="Influential Obs by Cooks distance")  # plot cook's distance
abline(h = 4*mean(cooksd, na.rm=T), col="red")  # add cutoff line
text(x=1:length(cooksd)+1, y=cooksd, labels=ifelse(cooksd>4*mean(cooksd, na.rm=T),names(cooksd),""), col="red") 
```
```{r}
influential <- as.numeric(names(cooksd)[(cooksd > 4*mean(cooksd, na.rm=T))])  # influential row numbers
head(num_df[influential, ])
```


```{r}
new_df = subset(num_df, select = c(curbweight, enginesize, stroke, compressionratio, horsepower, peakrpm, price))
df_remove_outlier <- new_df[-influential, ]
```

#### Model Removed Outliers
Decreased Residual standard error from 3237 to 2769
Decreased R^2 from 0.8407 to 0.8345
```{r}
lm_no_outlier=lm(price~curbweight+enginesize+stroke+compressionratio+horsepower+peakrpm,data=df_remove_outlier) 
summary(lm_no_outlier)
plot(lm_no_outlier)
```

#### Correlation 
```{r}
# improved correlation matrix
library(corrplot)

corrplot(cor(df_remove_outlier),
  method = "number",
  type = "upper" # show only upper side
)
```


#### Solution2: Log Transformation
Log(y) the model
```{r}
num_fit_log_with_outlier =lm(log(price) ~.,data=new_df)
summary(num_fit_log_with_outlier)
plot(num_fit_log_with_outlier)
```

Log(y) with the model that removed outliers.
```{r}
num_fit_log=lm(log(price)~curbweight+enginesize+stroke+compressionratio+horsepower+peakrpm,data=df_remove_outlier)
summary(num_fit_log)
plot(num_fit_log)
```


```{r}
sqrt(mean(resid(rm) ^ 2))
sqrt(mean(resid(num_fit_log_with_outlier) ^ 2))
sqrt(mean(resid(num_fit_log) ^ 2))
```

```{r}
sqrt(mean((num_df$price - fitted(rm)) ^ 2))
sqrt(mean((new_df$price - exp(fitted(num_fit_log_with_outlier))) ^ 2))
sqrt(mean((df_remove_outlier$price - exp(fitted(num_fit_log))) ^ 2))
```

#### Box-Cox Transformation

```{r}
boxcox(num_fit_log)
boxcox(num_fit_log, plotit = TRUE, lambda = seq(0.5, 1.5, by = 0.1))

plot(fitted(num_fit_log), resid(num_fit_log), col = "dodgerblue",
     pch = 20, cex = 1.5, xlab = "Fitted", ylab = "Residuals")
abline(h = 0, lty = 2, col = "darkorange", lwd = 2)
```

### Check Multicollinearity By Using Variance Inflation Factor (VIF)
After backward selection, we still need to check Multicollinearity and other assumptions. 
```{r}
library(carData)
#calculate the VIF for each predictor variable in the model
vif(num_fit_log)
```

```{r}
round(cor(df_remove_outlier), 2)
```

### t-test to remove enginesize
Ho: enginesize = 0 VS Ha: Not Ho
The result shows that we fails to reject the hypothesis which means enginesize can be removed.
```{r}
p_value = 0.09452
p_value_alpha = 0.05

t_ful = 1.680
t_split = 2.596

critical_value = 1.98

t_ful > critical_value
```

### Remove enginesize, peakrpm, and stroke due to Multicollinearity
```{r}
num_fit_log_rm_engsize=lm(log(price)~curbweight+stroke+compressionratio+horsepower+peakrpm,data=df_remove_outlier)
summary(num_fit_log_rm_engsize)
plot(num_fit_log)
```
#### Romove stroke
```{r}
temp=lm(log(price)~curbweight+compressionratio+horsepower+peakrpm,data=df_remove_outlier)
summary(temp)
plot(temp)
```
```{r}
temp=lm(log(price)~curbweight+compressionratio+horsepower,data=df_remove_outlier)
summary(temp)
plot(temp)
```



### Prediction Interval
```{r}
test[1,]
```
We are 95% confident that the price for the car with the information above will have a price between 17377.82 and 19009.76.
```{r}
conf = predict(temp, test[1,], interval="confidence")
exp(conf)

conf = predict(num_fit_log, test[1,], interval="confidence")
exp(conf)
```


### Test the model
Until this step I reliaze that I did not split the dataset to train and test dataset.
```{r}
p <- predict(temp, test)
test["num_predicted"] =round(exp(p),0)
test[,(ncol(test)-1):ncol(test)]


p <- predict(num_fit_log, test)
test["num_predicted"] =round(exp(p),0)
test[,(ncol(test)-1):ncol(test)]
```

```{r}
plot(round(test$num_predicted,0), test$price)
```










# Categorical Features
```{r}
cat_df <- read.csv(file = '/Users/chrisguan/Documents/Regression/final_project/Car_only/Car_only.csv')
cat_df = subset(cat_df, select = -c(X,doornumber, carbody))

cat_test = cat_df[rownames(test),]
cat_train = cat_df[rownames(num_df),]

#cat_test_rm_outlier <- cat_test[-influential, ]
cat_train_rm_outlier <- cat_train[-influential, ]
```



```{r}
test_merge <- merge(cat_test[-9], test,
                          by = 'row.names', all = TRUE)
test_merge = test_merge[-1]
test_merge
```


### Forwared Selection Manually
#### Indicator of carname

```{r}
df_remove_outlier
```

```{r}
carname_df =  subset(df_remove_outlier)
carname_df['car_region'] <- subset(cat_train, select = c(CarName))

amer=ifelse(carname_df$car_region=="america",1,0)
erp=ifelse(carname_df$car_region=="europe",1,0)
asia=ifelse(carname_df$car_region=="asian",1,0)

region_lm=lm(log(price) ~ curbweight + enginesize + stroke + compressionratio + horsepower  + peakrpm + amer + erp + asia,data=carname_df)
summary(region_lm)
plot(region_lm)
```

```{r}
c <- lm(log(price) ~ curbweight + compressionratio + horsepower + car_region , data=carname_df)
plot(c)
summary(c)
vif(c)
```



#### indicator of enginelocation
```{r}
eng_loc_df =  subset(df_remove_outlier)
eng_loc_df['enginelocation'] <- subset(cat_train_rm_outlier, select = c(enginelocation))

f=ifelse(eng_loc_df$enginelocation=="front",1,0)
b=ifelse(eng_loc_df$enginelocation=="rear",1,0)

eng_lm=lm(log(price)~curbweight + enginesize + stroke + compressionratio + horsepower  + peakrpm+f+b,data=eng_loc_df)
summary(eng_lm)
plot(eng_lm)
```


#### indicator of drivewheel
```{r}
wheel_df =  subset(df_remove_outlier)
wheel_df['drivewheel'] <- subset(cat_train_rm_outlier, select = c(drivewheel))

rwd=ifelse(wheel_df$drivewheel=="rwd",1,0)
four_wd=ifelse(wheel_df$drivewheel=="4wd",1,0)
fwd=ifelse(wheel_df$drivewheel=="fwd",1,0)


wheel_lm=lm(log(price)~curbweight + enginesize + stroke + compressionratio + horsepower  + peakrpm+rwd+four_wd+fwd,data=wheel_df)
summary(wheel_lm)
plot(wheel_lm)
```


#### indicator of aspiration
```{r}
asp_df =  subset(df_remove_outlier)
asp_df['aspiration'] <- subset(cat_train_rm_outlier, select = c(aspiration))

std=ifelse(asp_df$aspiration=="std",1,0)
turbo=ifelse(asp_df$aspiration=="turbo",1,0)

asp_lm=lm(log(price)~curbweight + enginesize + stroke + compressionratio + horsepower  + peakrpm+std+turbo,data=asp_df)
summary(asp_lm)
plot(asp_lm)
```


#### indicator of fueltype
```{r}
gas_df =  subset(df_remove_outlier)
gas_df['fueltype'] <- subset(cat_train_rm_outlier, select = c(fueltype))

gas=ifelse(gas_df$fueltype=="gas",1,0)
diesel=ifelse(gas_df$fueltype=="diesel",1,0)

gas_lm=lm(log(price)~curbweight + enginesize + stroke + compressionratio + horsepower  + peakrpm+gas+diesel,data=fueltype_df)
summary(gas_lm)
plot(gas_lm)
```


#### indicator of cylindernumber
```{r}
cyl_df =  subset(df_remove_outlier)
cyl_df['cylindernumber'] <- subset(cat_train_rm_outlier, select = c(cylindernumber))

small=ifelse(cyl_df$cylindernumber=="small",1,0)
middle=ifelse(cyl_df$cylindernumber=="middle",1,0)
large=ifelse(cyl_df$cylindernumber=="large",1,0)

cyl_lm=lm(log(price)~curbweight + enginesize + stroke + compressionratio + horsepower  + peakrpm+small+middle+large,data=cyl_df)
plot(cyl_lm)
summary(cyl_lm)
```

#### indicator of fuelsystem
```{r}
sys_df =  subset(df_remove_outlier)
sys_df['fuelsystem'] <- subset(cat_train_rm_outlier, select = c(fuelsystem))

mpfi=ifelse(sys_df$fuelsystem=="mpfi",1,0)
bbl2=ifelse(sys_df$fuelsystem=="bbl",1,0)
mfi=ifelse(sys_df$fuelsystem=="mfi",1,0)
bbl1=ifelse(sys_df$fuelsystem=="1bbl",1,0)
bbl4=ifelse(sys_df$fuelsystem=="4bbl",1,0)
idi=ifelse(sys_df$fuelsystem=="idi",1,0)
spdi=ifelse(sys_df$fuelsystem=="spdi",1,0)

sys_lm=lm(log(price)~curbweight + enginesize + stroke + compressionratio + horsepower  + peakrpm+mpfi+bbl2+mfi+bbl1+bbl4+idi+spdi,data=sys_df)
plot(sys_lm)
summary(sys_lm)
```
fuelsystem increased the r^2 the most, so we add cat fuelsystem to the nume dataset, and then remove p value greater than 0.05
```{r}
sys_lm=lm(log(price)~curbweight + enginesize + stroke + horsepower + peakrpm + mpfi + idi,data=sys_df)
plot(sys_lm)
summary(sys_lm)
```
```{r}
plot(sys_lm)
```



```{r}
catd = cat_train[,-9]
data_frame <- merge(num_df, catd,
                          by = 'row.names', all = TRUE)
data_frame = data_frame[,-1]
data_frame
```













### Forward Selection Package
```{r}
data_frame
```

Forward Selection based on p-value
```{r}
library(olsrr)
model<-lm(price ~.,data=data_frame)

FWDfit.p<-ols_step_forward_p(model,penter=.005)
FWDfit.p
```
```{r}
c <- lm(log(price) ~ enginesize + CarName  + cylindernumber + drivewheel + enginelocation + curbweight, data=data_frame)
plot(c)
summary(c)
```

#### Forward Selection Based on AIC
```{r}
model<-lm(price ~.,data=data_frame)
FWDfit.aic<-ols_step_forward_aic(model)

#This gives you the short summary of the models at each step
FWDfit.aic
```

```{r}
#if you want the intermediate steps, add set 'details' argument = TRUE
FWDfit.aic<-ols_step_forward_aic(model,details=TRUE)
FWDfit.aic
```




### The Best Outcome From Forward Selection
```{r}
best_forw <- lm(log(price) ~ enginesize + enginetype + CarName  + cylindernumber + drivewheel + enginelocation + curbweight + stroke + aspiration + 
          peakrpm + highwaympg + carheight,  data=data_frame)

summary(best_forw)
```

```{r}
plot(best_forw)
```


```{r}
p <- predict(best_forw, test_merge)
test_merge["foward_predicted"] =round(exp(p),0)
test_merge[,(ncol(test_merge)-1):ncol(test_merge)]
```

### Backward
```{r}
library(olsrr)
model<-lm(log(price)~.,data=data_frame)
BWDfit.aic<-ols_step_backward_aic(model)
BWDfit.aic

```
```{r}
c <- lm(log(price) ~ fuelsystem + carlength + carheight + enginesize + aspiration + wheelbase + peakrpm + highwaympg + citympg, data=data_frame)
plot(c)
summary(c)
```





























# Conclusion
After repeating the manual forward selection and auto forward selection ther are two possible outcomes. 

First, the two model eventually are very similar. Becasue they are using exactly same principle. Then we use this model as the best model and complete the project.

The second possible result is I decided to change the threshold of p-value for the auto farward selection and keep more variables. In this case, I can keep two models. One is the model with a strict p-value requirment, but the predict maybe not that accurate comparing with the model that has more complicated variables but not have a strict p-value requirement. One model is for everyday people and the another is for a relatively professional company that has more information about cars.  